\documentclass{beamer}

% \usepackage{beamerthemesplit} // Activate for custom appearance

\title{INFO411 Presentation \\ Streaming-Data Algorithms for High-Quality Clustering}
\author{Noel Park, Kat Lilly and Loren Kersey}
\date{\today}

\begin{document}

\frame{\titlepage}

\section[Outline]{}
\frame{\tableofcontents}

\section{Introduction, Background - Noel's bit}

\frame
{
  \frametitle{Introduction - Data stream model}
  
  Data stream models are mainly preferred when they are based around a large data stream:

  \begin{itemize}
    \item large volume of data is arriving continuously.
    \item unnecessary or impractical to store data in memory.
    \newline
  \end{itemize}

  Data stream models are mainly restricted by:
  \begin{itemize}
    \item in order access to data (as they arrive).
    \item small memory consumption.
    \newline
  \end{itemize}

  This paper by O'Callaghan et al. (2002) describes a streaming algorthim that effectively clusters large data streams.

  %NOTES:
  % 
  % dataset -> stored set of data, appropriate for clustering models that query data set again and again.
  % data stream -> approriate model when large volume of data arrives continuously
  % item 1: 
  % item 2: 
  % item 3: random access to memory not allowed.
  % item 4: limited amount of information can be stored.
  % challenge is to perform meaningful computations within these restrictions.
}

\frame
{
  \frametitle{Background - Related Works}
  

  %NOTES:
}

\section{The new algorithm described in this paper - Kat's bit}
\frame
{
  \frametitle{LSEARCH algorithm}

  \begin{itemize}
  \item  blah blah
  \end{itemize}
}

\section{Comparison with existing methods - Loren's bit}
\frame
{
  \frametitle{Their results relative to other methods...}

  \begin{itemize}
  \item stuff
  \item nonsense
  \item      
  \end{itemize}
}

\frame[t]{
  \frametitle{References}

  O'Callaghan, L., Mishra, N., Meyerson, A., Guha, S. \& Motwani, R. (2002). \textit{Streaming-data algorithms for high-quality clustering.} In proceedings of the 18th International Conference on Data Engineering. Available from: http://ieeexplore.ieee.org/document/994785/.
}
  
\end{document}
